RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-02-18 paper.tex
Trying to make some headway.

%% Abstract section.
\abstract{ Consider the emerging role of a data science team within an
  organization. Different data scientists and statisticians usually
  work on loosely related problems, and transition fluidly from
  exploratory data analysis to automated diagnostics and reports,
  which need to be deployed for wider consumption on the
  organization. There are two problems with the current
  practice. First, there is a gap in this workflow: EDA is performed
  with one set of tools, and automated reports and deployments with
  another. Second, current EDA environments mostly assume a
  single-developer perspective, while data scientist teams could
  greatly benefit from easier sharing of scripts, beyond that which a
  traditional version control system can provide. In this paper, we
  will present RCloud, a system designed to enable collaborative data
  analysis, visualization and deployment on the web. We will discuss
  the design decisions, tradeoffs and limitations, and compare it to
  current proposals.
} % end of abstract

@@

Kandel's interview study points out the typical ``explore'',
``model'', ``report'' cycle~\cite{Kandel:2012:EDA}. RCloud seeks to
reduce the impedance mismatch.

Heer and Agarwala identify a large number of design considerations for
collaborative visual analytics~\cite{Heer:2008:DCF}. \emph{Starring},
the system for signaling interest in notebooks, described in
Section~\ref{sec:starring}, addresses social-psychological incentives,
recommendation, and voting and ranking. RCloud's integrated deployment
mechanism, described in Section~\ref{sec:deployment}, adresses cost of
integration, content export, presentation and view sharing. Notebooks,
and the integrated version control system for them, described in
Section~\ref{sec:notebooks}, addresses modularity and granularity, and
artifact histories.

@@

>>>>

%% Abstract section.
\abstract{ Consider the emerging role of a data science team within an
  organization. Individual data scientists and statisticians usually
  work on loosely related problems, and must devise effective ways to 
  share their findings and to move results from exploratory data analysis
  to automated diagnostics and reports deployed for wider consumption.
  There are two problems with the current
  practice. First, there are gaps in this workflow: EDA is performed
  with one set of tools, and automated reports and deployments with another.
  Second, EDA environments often assume a single-developer perspective,
  while data scientist teams could greatly benefit from easier sharing of
  scripts and data feeds, experiments, annotations, and automated
  recommendations, which are well beyond what traditional version control
  systems provide.  In this paper, we propose RCloud, a system that supports
  collaborative data analysis, visualization and web deployment. We will
  discuss the design decisions, tradeoffs and limitations, and compare RCloud
  to other current proposals.
} % end of abstract

@@

Kandel's interview study points out the typical ``explore'',
``model'', ``report'' cycle~\cite{Kandel:2012:EDA}. RCloud seeks to
reduce the impedance mismatch. Kandel et al point out that larger teams
are becoming more common in data analysis, that supporting
collaboration is a difficult and important problem, and that
sharing and versioning of data sources and artifacts was hindered
by technology.  ``We found that analysts typically did not share scripts
with each other. Scripts that were shared were disseminated similarly to
intermediate data: either through shared drives or email.
Analysts rarely stored their analytic code in source control.''
Their work points to the need for better technology to support
these aspects of data analysis in teams.

Heer and Agarwala identify a large number of design considerations for
collaborative visual analytics~\cite{Heer:2008:DCF}. \emph{Starring},
the system for signaling interest in notebooks, described in
Section~\ref{sec:starring}, addresses social-psychological incentives,
recommendation, and voting and ranking. RCloud's integrated deployment
mechanism, described in Section~\ref{sec:deployment}, addresses cost of
integration, content export, presentation and view sharing. Notebooks,
and the integrated version control system for them, described in
Section~\ref{sec:notebooks}, addresses modularity and granularity, and
artifact histories.

Our work has been inspired or has benefited from other modern technologies
to improve the data analysis environments and processes, such as RStudio,
R packages such as Markdown, knitr and Shiny, and iPython notebooks, to name a few.  % explain

@@

% limitations
Previous studies have pointed out frequent difficulties in the
achieving production-level flexibility, scalability and maintainability
with experimental code created by data analysts.  These properties cannot
be ensured by any programming environment, but a reasonable approach in
general is to provide suitable tools that make it easier for well-intentioned
programmers to adopt such practices.

% security issues
